\hspace{-0.1cm}{J-ReCoVer}:~Java~Reducer~Commutativity~Verifier

### 2019-06-24 draft.tex
Section 4.3

%=============================================================================
\subsection{Optimization: Live Variable Analysis} \label{section:optimizations}
%=============================================================================

Here we explain how live variable analysis is used in J-ReCoVer to improve the precision of commutativity checking.

We find that in many cases, Equation~(\ref{eq:commu}) is a condition that is too strong for the reducer to be commutative. For instance, consider a simple example. In the loop body, the input is first stored in a variable $t$ and then added to $s$. 
That is $t:=\cur;s:=t$.
After the loop, output the value of $s$.
In this case, the $F$ function returns the updated values of both $s$ and $t$ after the execution of the loop body. Observe that
$F(c_1, F(c_2,s,t)) = (c_1+c_2, c_1)$ and $F(c_2, F(c_1,s,t)) = (c_1+c_2, c_2)$. It follows that the corresponding Equation~(\ref{eq:commu}) is invalid. The second component of the returned tuples corresponds to the value of $t$ after executing the loop body twice. Their values are $c_1$ and $c_2$, respectively, in $F(c_1, F(c_2,s,t))$ and $F(c_2, F(c_1,s,t))$. However, in this case, the value of $t$ will not affect the output of this reducer.
To handle this issue, we perform a simple backward live variable analysis to collect all variables whose value may propagate to the output command after the loop execution. Only these variables are required to be equivalent. In our evaluation, the ratio of examples that our approach can successfully analyze is significantly increased from $6.8\%$ to $97.5\%$ with the help of this optimization.

>>>>

%=============================================================================
\subsection{An Optimisation by Live Variable Analysis}
\label{section:optimizations}
%=============================================================================

We now explain how a simple live variable analysis is used in J-ReCoVer to
significantly improve the precision of commutativity checking.

In our initial experiments, we realised that Formula~\ref{eq:commu} is a
condition that is too strong for the reducer to be commutative. To illustrate
the issue, we present a simple example. In the loop body, the input is first
stored in a variable $t$ and this is then assigned to $s$, i.e., $t:=\cur;s:=t$.
After the loop, the value of $s$ is output. In this case, the $F$ function
returns the updated values of both $s$ and $t$ after the execution of the loop
body. Observe that $F(c_1, F(c_2,s,t)) = (c_1+c_2, c_1)$ and $F(c_2, F(c_1,s,t))
= (c_1+c_2, c_2)$. It follows that Formula~\ref{eq:commu} is invalid. The second
component of the returned tuples, which causes the invalidity, corresponds to
the value of $t$ after executing the loop body twice. Their values are $c_1$ and
$c_2$, respectively, in $F(c_1, F(c_2,s,t))$ and $F(c_2, F(c_1,s,t))$. However,
in this case, the value of $t$ will not affect the output of the reducer.

To handle the above issue, we perform a simple backward live variable analysis
to collect all variables whose value may propagate to the output command after
the loop execution. Only these variables are then required to be equivalent. In
our evaluation, the ratio of reducers that our approach can successfully analyze
is significantly increased---in particular, from $6.8~\%$ to $97.5~\%$---by
using this optimisation.
